### 2015-03-02 fundamentals/impl.tex

All of the public interface (the \gls{API}) must be documented as required by the \Cyclus
\gls{QA} policy. This certifies that the intention for a code unit is communicated
in way that is separate from its implementation. This policy is important
because implementations are often wrong and do not reliably communicate their intent. Truly trustworthy communication about what
software should be doing occurs when the author explicitly states the
goals of an \gls{API} in prose form. Future developers are then able to
compare the implementation versus the documentation to discern whether or not
these are in agreement. Documentation is thus a secondary higher-level information
stream.  In \Cyclus, this information is aggregated together into static
websites with the Doxygen \cite{van_heesch_doxygen:_2008} and Sphinx
\cite{brandl_sphinx_2014}
tools, and can be accessed at \url{http://fuelcycle.org}.

>>>>

All of the public interface (the \gls{API}) must be documented as required by
the \Cyclus \gls{QA} policy. This certifies that the intended goals of an
\gls{API} are communicated explicitly by the author in prose form.  In \Cyclus,
this information is aggregated together into static websites with the Doxygen
\cite{van_heesch_doxygen:_2008} and Sphinx \cite{brandl_sphinx_2014} tools, and
can be accessed at \url{http://fuelcycle.org}.
